---
title: "Chapter 1"
format: html
editor: source
---

## Introduction to R

### **Math in R**

* Anytime R is showing you a + and not a > that means it's waiting for you to finish a command

* Math commands in R:

  + Parentheses: (, )
  + Exponents: ^ or **
  + Multiply: *
  + Divide: /
  + Add: +
  + Subtract: -
  + 5e3 for scientific notatio

### **Variables and Assignments**

* If you do x <- 1/40 that will mean x = 0.025

* Now you can do equations with x
  + Like log(x)

* Variable names can contain letters, numbers, underscores and periods but no spaces

 * Make sure to be consistent if you are using
 
  + periods.between.words
  + underscores_between_words
  + camelCaseToSeparateWords
  
### **Mangaing your environment**

* ls() will list all of the variables and functions stored in the global environment
  + To list all variables, you can write ls(all.names=TRUE)

* You can use rm() to get rid of objects you no longer need

### **Installing Packages**

* See what packages you have installed: installed.packages()

* You can install packages by typing install.packages("packagename")

* You can update installed packages by typing update.packages()

* You can remove a package with remove.packages("packagename")

* You can make a package available for use with library(packagename)

* You can also do this all in packages tab

  


When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
