---
title: "Chapter 2"
format: html
editor: source
---

## Project Management in R Studio

### **Intro to Project Management**

* Why project management and organization is important:
  + It will help ensure the integrity of your data
  + It makes it simpler to share your code with someone else (a lab-mate, collaborator, or supervisor)
  + It allows you to easily upload your code with your manuscript submission
  + It makes it easier to pick the project back up after a break
  
### **Organizing Data**

* Creating a project:
  + Click the “File” menu button, then “New Project”
  + Click “New Directory”
  + Click “New Project”
  + Type in the name of the directory to store your project, e.g. “my_project”
  + If available, select the checkbox for “Create a git repository.”
  + Click the “Create Project” button
  
#### Best Practicies for Organizing Data

1. Treat Data as read only: make it easy to read with hashtags explaining what each code is doing and also making it nicely formatted

2. Data cleaning: storing scripts in a seperate folder and creating a read-only folder with the cleaned datasets

3. Generating output as disposable: have an output folder with subcategories for each seperate analysis

4. Put each project in its own directory, which is named after the project

5. Put text documents associated with the project in the doc directory

6. Put raw data and metadata in the data directory, and files generated during cleanup and analysis in a results directory

7. Put source for the project’s scripts and programs in the src directory, and programs brought in from elsewhere or compiled locally in the bin directory.

8. Name all files to reflect their content or function

### **Saving Data in Data Directory**

* 

### 


```{r}
head(gapminder_data)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
