---
title: "Chapter 3"
format: html
editor: source
---

## Seeking help

### **Reading Help Files** 

* General way to find help on R: 
  - ?function_name
  - help(function_name)
  
* Each help page is broken into a subscription
  - Description: An extended description of what the function does
  - Usage: The arguments of the function and their default values (which can be changed)
  - Arguments: An explanation of the data each argument is expecting
  - Details: Any important details to be aware of
  - Value: The data the function returns
  - See Also: Any related functions you might find useful
  - Examples: Some examples for how to use the function

### **Special Operators**

* To seek help from specific operators, use quotes or backticks:
  - ?"<-"
  - ?`<-`
  
### **Getting Help with Packages**

* Many packages come with “vignettes”: tutorials 
* Vignettes: long-form guide to a package
* vignette(package="package-name") will list all available vignettes for package-name, and vignette("vignette-name") will open the specified vignette.
* If a package doesn’t have any vignettes, you can usually find help by typing help("package-name")
* RStudio also has cheatsheets: https://posit.co/resources/cheatsheets/

### **When You Remember Part of the Function Name**

* When you don't know what package a function is in, you can write:
  - ??function_name
* It will tell you it back. like you know "set" is in it:
  - ??set
  




  


```{r}
?(write.table)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
